NumPy---Array Computation for Python

### 2019-12-20 body.tex
More work on intro

Before NumPy, two different Python array packages—Numeric and
numarray—existed.  The first was developed by Jim Fulton, Jim Hugunin, Paul Dubois, Konrad
Hinsen, Travis Oliphant, and others, and was aimed at fast manipulation of many
small arrays.  In contrast, to handle large astronomical images,
NumArray was developed at the Space Telescope Science Institute (STScI).
These array objects had different strengths and weaknesses, and therefore
divided the already small community.  Furthermore, the divide
posed a challenge for SciPy, which was built on Numeric and provided
fundamental scientific routines.
In response, the maintainer of Numeric, Travis Oliphant, started a
major rewrite that aimed to be a ``best of both worlds'' unification
of the two projects.  This became known as NumPy.

This spurred renewed development in both SciPy and NumPy and 
heralded the current era of wide-spread use of Python for scientific computing.
To coordinate work as a global community, to ensure accuracy of computed
results, and to allow modification without breakage, the NumPy (and SciPy) community
pioneered best software engineering practices in the scientific Python
community  \cite{millman2014developing}.
For example, NumPy early on adopted distributed revision control, unit testing,
continuous integration, code review, and standardized executable documentation.
It also developed a standard for ``docstrings''—text describing each NumPy function.
This quickly became the standard for the larger scientific Python community.

>>>>

Before NumPy, two different Python array packages—Numeric and NumArray—existed.
The first began in the mid-90s and was developed by Jim Fulton, Jim Hugunin,
Paul Dubois, Konrad Hinsen, Travis Oliphant, and others, and was aimed at fast
manipulation of many small arrays.
By the beginning of the millennium, several libraries built on top of Numeric 
the provided fundamental scientific routines `were combined to form SciPy.
Due to the poor performance of Numeric on large data sets, NumArray was
developed at the Space Telescope Science Institute (STScI) to handle
large astronomical images such as those produced by the Hubble Space Telescope.
It was initially considered the successor to Numeric.
However, it performed poorly on small arrays.
This divide posed a challenge for SciPy as it wasn't clear how to support
both libraries.
Working with the NumArray and SciPy community, the maintainer of Numeric,
Travis Oliphant, started a major rewrite that aimed to be a ``best of both
worlds'' unification of the two projects.  This became known as NumPy.

The creation of NumPy spurred renewed development in both SciPy and the larger
scientific Python ecosystem and heralded the current era of wide-spread use of
Python for scientific computing.
To coordinate work as a global community, to ensure accuracy of computed
results, and to allow modification without breakage, the NumPy (and SciPy) community
pioneered best software engineering practices in the scientific Python
community  \cite{millman2014developing}.
For example, NumPy early on adopted distributed revision control, unit testing,
continuous integration, code review, and standardized executable documentation.
It also developed a standard for ``docstrings''—text describing each NumPy function.
This quickly became the standard for the larger scientific Python community.
